
\section{Work-related projects}

\denseouterlist{
    \entry
    {\href{https://www.aparat.com/atrovan.com}{Indoor IR controller}}

    {\textendash Inside smart Home devices, some devices were invented to automate or make smarter older devices. in all of our houses, we have devices that control IR remotes like the TV, Receiver, and Air-conditioner ...  and each of them has a remote control. So what if we replace all of that remotes with just one mobile application and a device that could play the role of all those remote controls? this project was based on STM32F1 and ESP8266, which connected with UART protocols. The esp was responsible for connecting to the server and communicating with the mobile application, and the ARM part was in the role of learning and regenerating the IR signals. during my master's, I was involved with this project as an embedded developer, and I was responsible for developing the ARM code.}
    
    \entry
    {\href{http://babt.ir/en/gps-software/}{Multifunctional Vehicle Tracker}}
    
    {\textendash 
    Inside Iran, it's so typical that people equip their cars with an alarm system when they buy a new car. So when the market arises a need companies start to fill that gap. the car tracker among other car alarm systems, has the advantage that could be more secure, so if a company could design that inside market could be a winner. so the main challenge inside this project is being full of features compared to others and being cost-effective. we could choose so many GSM-GNSS modules like that company like Quectel, Simcom, AiThinker, Simware, OpenLuat, etc but if we get deeper, we could understand that these modules are based on some SoCs. among these SoC, MT2503 from MediaTek could satisfy our goal because it could support both GSM and GNSS with MediaTek firmware. our company bought that firmware from a Chinese company named {\href{http://www.new-mobi.com/product/showproduct.php?lang=en&id=28}{new-mobie}} and their modules the only problem with this Soc is the lack of documentation and development community around it. after my master I was 
    (note: Holtek, Accelerometer, flash, sound, Camera,)
    }
    
}
