\section{Education}

\outerlist{

\entrybig
{\textbf{Amirkabir University of Technology
\href{https://www.topuniversities.com/universities/amirkabir-university-technology}{(QS Global World Ranking)}}}{Tehran, Iran}
{M.S. in Electrical Engineering, Digital Electronics, Overall GPA: 17.00/20.00}{2018\textendash2021}
\innerlist{
  \entry{Thesis: "Analysis of data received from vehicles, for driver behavior profiling on the computing cloud"}
    {
    \textendash \textbf{Supervisor} :
    \href{https://scholar.google.com/citations?user=dE_BwesAAAAJ&hl=en}{Dr. Seyed Ahmad Motamedi}
    }
    {\href{https://drive.google.com/file/d/1_X8rFgTpEOOmOKAuPuurI5aJom0gaGq9/view?usp=sharing}{\color{gray}\scriptsize{ -Thesis in Persian}}}
}

% \large{\textbf{d:}}
\denseouterlist{
    \entry
    {\href{https://github.com/HosseinlGholami/Event-Extraction}{Analysis of Data Received from Vehicles for Driver Behavior Profiling on the Cloud:}}
    {Developed a model that detects harsh driving events, such as abrupt braking and acceleration, using accelerometer and gyroscope data. Implemented a sliding window approach alongside decision tree models and integrated a dynamic time warping (DTW) algorithm for real-time processing with microcontrollers.}

    \entry
    {\href{https://drive.google.com/file/d/1w7lotKGIPuQXmhTb_Bw9BShT6hqA5uw6/view?usp=sharing}{Cloud-Based Event Transmission and Storage:}}
    {Engineered a server application to efficiently receive and store MQTT packets, utilizing RabbitMQ as the message broker and Redis for temporary data storage. Architected the system using Docker containers to ensure seamless deployment, and developed a driving simulator application for data collection on driver behavior.}

    \entry
    {\href{https://github.com/HosseinlGholami/BehavePart}{Driver Behavior Analysis for Trip Grading:}}
    {Performed statistical analyses on collected driving data to grade individual trips and evaluate driver behavior. Designed a system to calculate insurance rates based on driving habits, promoting safer driving practices.}
}

\entrybig
{\textbf{K. N. Toosi University of Technology 
\href{https://www.topuniversities.com/universities/khajeh-nasir-toosi-university-technology/undergrad}{(QS WUR By Subject Ranking)}}}{Tehran, Iran}
{B.S. in Electrical Engineering, Electronics, GPA: 16.25/20.00}{2014\textendash2018}
{Last two years GPA: 17.18/20.00}
\innerlist{
  \entry{Thesis: "Implementation of cloud switches supporting the measurement of power, temperature, and humidity through MQTT protocol"}
    {
    \textendash \textbf{Supervisor} :
    \href{https://scholar.google.com/citations?user=ci-Y5v8AAAAJ&hl=en}{Dr. Amir Mousavinia}
    }
    {\href{https://drive.google.com/file/d/1kxL_jlBAUOAer3QEUS4yO_IW3CJmjpNL/view}{\color{gray}\scriptsize{ -Thesis in Persian}}}
}

% \large{\textbf{B.S. Projects:}}
\denseouterlist{
    \entry
    {\href{https://github.com/HosseinlGholami/B.s.c-prj}{Implementation of Cloud Switches Supporting Power, Temperature, and Humidity Measurement via MQTT Protocol:}}
    { Designed and implemented a socket with two 10A outputs controlled through an MQTT dashboard. Integrated ACS712 sensors for measuring power consumption and DHT22 sensors for reporting temperature and humidity. Utilized the ESP32 as the main processor, with \href{https://www.cloudmqtt.com}{CloudMQTT} serving as the message broker and the MQTT Dash Android app for real-time monitoring. \scriptsize{\color{gray}{\href{https://drive.google.com/drive/folders/1ICIlKOc84qtPh1K8paZ4Qa0Qw9R8SjDF?usp=sharing}{Demo-video}}}}
    }
}
\vspace{+0.00cm}
